Monte Carlo tree search compared to A\(^*\) in airspace configuration decision problem

### 2018-05-15 article/article.tex
(~) correktur
(+) Paragraph of shame

\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{unicode-math}
\usepackage{amsmath,amsthm,stmaryrd}
\usepackage{algorithm,algpseudocode}
\usepackage{paralist}
\usepackage{titlesec}

@@

\paragraph{Expansion (algorithm~\ref{alg:expansion})}
If the selected node has one or more unvisited children, the selection stops and
one of them is added to the search tree randomly, the latter being thus expanded
by this new node.
\begin{algorithm}
  \caption{Expansion}\label{alg:expansion}
  \begin{algorithmic}
    \Function{Expand}{$v$}
    \State{}$\ell \gets \{ v | v \text{\,children of\,} u, T_v = 0 \}$
    \State{}\Return{random element from $\ell$}
    \EndFunction{}
  \end{algorithmic}
\end{algorithm}

@@

\subsection{Theoretical performances}
In this paper, a high branching factor problem is considered.

@@

TODO

>>>>

\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{unicode-math}
\usepackage{amsmath,amsthm,stmaryrd}
\usepackage{algorithm,algpseudocode}
\usepackage{paralist}
\usepackage{titlesec}
\usepackage{tikz,pgfplots}

@@

\paragraph{Expansion (algorithm~\ref{alg:expansion})}
If the selected node has one or more unvisited children, the selection stops and
one of them is added to the search tree randomly, the latter being thus expanded
by this new node.
\begin{algorithm}
  \caption{Expansion}\label{alg:expansion}
  \begin{algorithmic}
    \Function{Expand}{$u$}
    \State{}$\ell \gets \{ v | v \text{\,children of\,} u, T_v = 0 \}$
    \State{}\Return{random element from $\ell$}
    \EndFunction{}
  \end{algorithmic}
\end{algorithm}

@@

\subsection{Theoretical performances}\label{ssec:theoretical_performances}
In this paper, a high branching factor problem is considered.

@@

\subsection{Experimental setup}
For the tests, the Paris West area is used. It contains 12 elementary modules
and 20 control sectors. The resulting model tree has a mean branching factor of
16. Since it is the smallest French area, considering the already important
branching factor, a stochastic tree search method seems appropriate.

\subsection{Accuracy}
Accuracy is assessed by comparing the exact cost given by the A\(^*\) algorithm
with the result of the MCTS\@. The time allowed to the MCTS to run is considered
long enough to allow the MCTS to converge to its best solution.

It results in figure~\ref{fig:longterm} that the algorithm described here has a
bias of approximately 15\%, considering that the stabilisation matches the
optimal value reachable.

Considering paragraph~\ref{ssec:theoretical_performances}, the MCTS should
eventually converge to the optimal value, and this result reveals a flaw in the
implementation of the algorithm.
\begin{figure}
  \begin{tikzpicture}
    \begin{axis}
      [line width=0.05, mark size=0.1, xlabel=time(s), ylabel=cost]
      \addplot+ table {data/longterm.data};
      \addplot+[dashed, domain=0:10] {1268};
    \end{axis}
  \end{tikzpicture}
  \caption{The continuous line shows the total cost of a path computed by the
    MCTS algorithm. The x-axis shows the time allowed to the algorithm. The
    dashed curve is 15\% of the optimal cost found with the \(A^*\)
  algorithm.}\label{fig:longterm}
\end{figure}

\subsection{Speed}
To measure

\subsection{Further work}
